---
title: "Election"
author: "Rajeev Kumar Yadav"
format: html
execute: 
  echo: false
---


```{r}
#| label: setup
#| message: false

library(primer.data)
library(tidyverse)
library(brms)
library(tidybayes)
library(gtsummary)

x <- governors |> 
  select(death_age, election_age, win_margin, sex, party) |> 
  mutate(treatment = ifelse(win_margin > 0, "win", "lose")) |> 
  filter(abs(win_margin) < 5)
```


Using data about US Governor candidates from years 1945 - 2012, we seek to find the relationship between the longevity of Mayor and whether or not he wins Mayoral election. We have concerns that average life span have increased over the years which might affect our results. We modeled age at death to sum of election results, political party affiliation, and win margin. We expect the winning candidates to live an extra 8 years on average (+-6 years).

```{r}
#| label: model
#| cache: true

fit_elec_2 <- brm(formula = death_age ~ treatment + win_margin
                 + party,
                  data = x,
                  family = gaussian(),
                  refresh = 0,
                  silent = 2,
                  seed = 9)

```


$$death\_age = \beta_{0} + \beta_{1} treatment_i + \beta_{2}win\_margin_i + \\
\beta_{4}repub_i + \beta_{5}thirdparty_i + \epsilon_{i}$$


```{r}
#| warning: false
tbl_regression(fit_elec_2)
```

